Rusty Linux: Advances in Rust for Linux Kernel Development

### 2024-06-01 paper.tex
Update on Overleaf.

Rust, a systems programming language developed by Mozilla, has garnered significant attention for
its strong emphasis on memory safety without sacrificing performance. Rust's ownership model and its
compile-time checks effectively prevent common programming errors that lead to security
vulnerabilities. What makes Rust unique is the fact that it accomplishes these tasks without the use
of a garbage collector, making it an ideal candidate for kernel development where safety and
performance are critical.

>>>>

Rust, a systems programming language developed by Mozilla, has garnered significant attention for
its strong emphasis on memory safety without sacrificing performance. Rust's ownership model and its
compile-time checks effectively prevent common programming errors that lead to security
vulnerabilities. What makes Rust unique is the fact that it accomplishes these tasks without the use
of a garbage collector, making it an ideal candidate for kernel development where safety and
performance are critical.~\cite{}
